
% ======================================================================
% ABSTRACT
% ======================================================================
\setstretch{1.5}
\begin{center}
{\fontsize{16}{19}\selectfont\textbf{Abstract}}
\end{center}

\vspace{3mm}

Large language models (LLMs) are developing rapidly, opening up new paths for enterprise digital transformation. However, applying them in regulated domains such as banking presents significant challenges that remain to be addressed. For example, generated code may be incorrect, domain knowledge can be outdated or unverifiable, enterprise tools may be invoked unreliably, and reliance on external APIs introduces data sovereignty risks. To solve these issues, this paper proposes a system and implementation method specifically designed for digital transformation of banks.

The platform integrates three specialized agents: a Code Agent that converts natural language into SQL through a Python LLM inference service with multi-level whitelist validation, a Retrieval-Augmented Generation (RAG) Agent that retrieves policy knowledge using Milvus vector indexing and vLLM generation, and a Tool Agent that handles everyday business tasks such as meeting room booking, schedule conflict detection, and route planning. A unified Copilot dispatcher sits above all three agents, classifying user intent from a single natural language interface and routing each request to the appropriate agent.

The platform enforces role-based access control (RBAC) with multiple security tiers and department-level data isolation. Its five-layer microservices architecture spans a Vue 3 frontend, Spring Cloud Gateway, Spring Boot business and AI services, and a multi-engine data layer, all deployed via Docker Compose.

\newpage
