% APPENDIX C: USER MANUAL AND DEPLOYMENT GUIDE
% ======================================================================
\newpage
\begin{center}
{\fontsize{16}{19}\selectfont\textbf{Appendix C: User Manual and Deployment Guide}}
\end{center}

\vspace{3mm}

\subhead{C.1 Online Demo}

A live deployment of the platform is accessible at \texttt{https://bankagent.online}. This instance runs on a DigitalOcean Droplet with 2 vCPUs and 8 GB RAM. Given the resource constraints of a single shared server, the following limitations apply. The RAG embedding worker and Milvus vector database may respond more slowly than in a production environment, particularly during concurrent queries or full index rebuilds. The frontend build is served from a single Nginx instance without a CDN. The server may occasionally become unavailable during maintenance or if resource limits are reached. These limitations are inherent to a project demonstration deployment. In an enterprise production setting, each service would run on dedicated hardware with Kubernetes orchestration, autoscaling, and redundant storage, and the platform would comfortably handle its designed concurrency targets.

\subhead{C.2 Local Deployment}

For the most responsive experience, evaluators may deploy the platform locally using Docker Compose. The following steps summarize the process.

\textbf{Prerequisites.} Docker Desktop and Node.js must be installed. 16 GB RAM is recommended; the full stack runs 15 containers including Milvus, five Java microservices, two Python workers, Nginx, and supporting infrastructure. On machines with less RAM, the RAG Agent and embedding worker can be disabled by commenting out the corresponding services in \texttt{docker-compose.yml}; the remaining platform will operate normally.

\textbf{Startup.} The following commands build and start the platform:

\begin{lstlisting}
cd web-ui
npm install && npm run build
cd ..
docker compose up --build -d
\end{lstlisting}

The first build takes 15--30 minutes. Docker must pull base images, compile the five Java services from source, and download the BGE-M3 embedding model (approximately 2 GB) inside the worker container. Subsequent starts take only a few seconds. Once all containers show \texttt{healthy} or \texttt{Up} status in \texttt{docker compose ps}, open \texttt{http://localhost} in a browser.

\textbf{Test accounts.} The following accounts are pre-seeded in the database:

\begin{table}[H]
\small\singlespacing
\centering
\caption{Pre-Seeded Test Accounts}
\label{tab:test-accounts}
\begin{tabularx}{\textwidth}{>{\RaggedRight\arraybackslash}p{0.25\textwidth}>{\RaggedRight\arraybackslash}p{0.18\textwidth}>{\RaggedRight\arraybackslash}X}
\toprule
\textbf{Username} & \textbf{Password} & \textbf{Role} \\
\midrule
admin & 123456 & System Administrator (clearance Level 3) \\
credit\_mgr & 123456 & Credit Department Manager (Level 2) \\
credit\_staff & 123456 & Credit Department Staff (Level 1) \\
compliance\_mgr & 123456 & Compliance Department Manager (Level 2) \\
compliance\_staff & 123456 & Compliance Department Staff (Level 1) \\
\bottomrule
\end{tabularx}
\end{table}

\subhead{C.3 Navigating the Platform}

\textbf{Main Dashboard.} Displays a welcome message, a pending approval alert banner for administrators, and a statistics overview. The Copilot floating widget (blue icon, bottom-right corner) is accessible from every page and serves as the unified natural language interface. Users can type a question into the Copilot to query databases, search policies, book meeting rooms, or plan routes without navigating to a specific agent page.

\textbf{Tool Agent (/app/tool).} Three tabs: Meeting (room search with date and capacity filters, and booking), Schedule (conflict detection by attendee with a visual timeline), and Route (origin and destination input with Amap map rendering and step-by-step guidance).

\textbf{Code Agent (/app/code).} A three-step workflow: enter a natural language query, review the generated SQL in a code editor, then execute and view results in a paginated data table. If the SQL fails any validation layer, a security rejection message is displayed.

\textbf{RAG Workbench (/app/rag).} Users can ask policy and document questions. The page displays generated answers with citations showing document identifiers, snippets, and similarity scores. Administrators can rebuild the full RAG index or reprocess individual documents. Users can submit access requests for documents outside their clearance scope.

\textbf{Documents (/app/dept-docs).} Two tabs: System Manuals (global documents) and Department Assets (clearance-controlled). Documents beyond the user's clearance level show ``Access Restricted'' with an option to apply for access via the HITL escalation workflow.

\textbf{Messages (/app/notification).} A three-column layout with filters (All, Unread, Pending Approvals, Sent). Type-specific renderers handle RAG\_APPLY approvals with approve/deny buttons, SQL\_AUDIT records with SQL code blocks, and BUG\_REPORT feedback.

\textbf{Registration (/register).} New users register with an email-format username and a 6-digit verification code delivered via the Resend API. Rate limiting enforces a 60-second cooldown between code requests and a daily cap per email address.

\textbf{Administration (/app/admin/users, /app/admin/resources, /app/admin/my-dept).} User Management provides a searchable table with role assignment, account status toggling, clearance level adjustment, and department assignment. Resource Management lets administrators manage meeting rooms and view all schedules. My Department (for ROLE\_DEPT\_ADMIN) shows members within the administrator's own department.

\textbf{Settings (/app/settings).} Profile editing and password change dialogs.

\newpage

% ======================================================================
