% CHAPTER 2: LITERATURE REVIEW
% ======================================================================
{\fontsize{18}{22}\selectfont\textbf{2 Literature Review}}\par

\vspace{3mm}

\subhead{2.1 LLMs in Enterprise Applications}

Transformer-based LLMs have changed AI research and its uses. Vaswani and others (2017)[9] introduced the transformer architecture. Since then, this field gain a rapid progress, large models, like GPT family, have shown strong few-shot and zero-shot skills in many tasks. But a big gap still exists. There is a gap between being able to answer pretty general questions and being reliable enough to handle business tasks.

In some specificated organizions, LLMs are used to automatically manage knowledge intensive works, including report writing, document abstract generating, programming code making, specificated field question answering (QA). But no matter what natural language processing task, when these models are put into business use, three main problems appear: (1) they get facts wrong (hallucination), (2) their knowledge base stays fixed and cannot be changed, (3) handling data privacy is always difficult, in fact many businesses are not comfortable sending their proprietary data to public APIs.

Financial services industry has a strick attitude on using AI. Banks must meet the regulation commands. They need to standardize data confidentiality, transaction aduit, and explanatory automate decisions. That's why there is a growing interest in localy stored AI that keeps data within the bank's own system.

\subhead{2.2 Multi-Agent Systems and Orchestration}

Multi agent systems (MAS) originated from research focus on distributed artificial intelligence. Early systems used rule-based agents, which had fixed interaction rules. As LLMs are becoming more and more wide spread, the MAS model has undergone a great change in recent years. Modern multi-agent frameworks use LLMs for agent reasoning. Instead of using hard-coded scripts, agents now use natural language.

Wu et al. (2023) proposed AutoGen [4]. This platform allows different LLM-driven agents to communicate, and work together to solve complex questions. AutoGen has a dynamic conversation machanism, which supports many different communication patterns. It includes one-to-one dialogs and group conversations. The important parts of the design are: agents can take different roles (like assistant, reviewer, or coder). This role separation lets the system have a built-in checks and balances system. For example, one agent generates SQL and another reviews the generated SQL code.

Hong et al. (2023) proposed MetaGPT [5]. This is a meta programming framework that applies Standardized Operating Procedures (SOPs) to multi-agent collaboration. They specifically defined roles for agents like Product Manager and Architect. This setup added a layer of process control to the already flexible agent interactions.

These frameworks show promising results in research settings. However, there's still a gap between flexible, role-based multi-agent systems and production systems in banking environments. For process standardization, systems must present deterministic behaviors and tight security controls.

\subhead{2.3 Code Generation and Text-to-SQL}

Converting natural language questions into executable SQL statements has been a major challenge in the field of natural language processing for over 20 years. The early solution adopted a rule-based approach with intermediate representation, relying on hand-made grammar rules to map natural language to SQL syntactic structures. While highly accuate in limited domains, these methods are hard to scale across different databases and domains.

The emergence of the Spider dataset is an important development in this field. Yu et al. (2018) [1] constructed this dataset. Spider is a cross domain large-scale test set that includes 10181 query expressions and 5693 unique complex SQL queries. They cover 138 different domains and 200 databases. One significant feature of Spider is its focus on complex queries involving multiple table joins, nested subqueries, and set operations. These are the exact types of queries that enterprise business analysts often need in real business scenarios. The dataset has become a standard model for evaluating Text-to-SQL systems, and its design directly influenced how we think about code generation in our code agent's prompt engineering and test case design.

In terms of deployment approach, the fully local ONNX-based inference solution was first considered a better option for code generation tasks due to its data security advantages. However, considering the need for a balance between reasoning capability, throughput, and engineering complexity, this project will eventually adopt a Python-based inference server with HTTP communication. This design lets the Java-based agent service use the Python ecosystem's LLM capabilities through simple REST calls. It also keeps all data inside the Docker network.

\subhead{2.4 RAG}

RAG fixed a weakness in LLM. LLM relies on the static knowledge stored in its parameters. This knowledge often leads to factual errors. Lewis et al. (2020) [8] first described RAG. The RAG design has two main parts: a retriever and a generator. When a user asks a question, the retriever first finds relevant documents from a knowledge base. Then, the generator includes the retrieved context in the prompt and produces an answer based on the retrieved information. This approach provides verifiability---the answer can be linked back to the source documents.

A typical RAG workflow has three phases. Phase one is indexing. In indexing, source materials are split into segments. These segments are turned into vector embeddings. This uses a pre-trained encoder model. The embeddings are stored in a vector database. Typical vector databases are Milvus or Pinecone. Phase two is retrieval. The user's question is turned into the same embedding space. An approximate nearest neighbor (ANN) search is performed to retrieve the top-K most similar segments. Phase three is generation. The retrieved segments are formatted into a structured prompt. They are combined with the original question. The prompt is sent to the LLM. The LLM generates an answer.

In banking, RAG is useful. This is because regulatory rules, internal policies, and product documents are kept in large text stores. These stores are updated often. They cannot be put into model weights by fine-tuning. However, bank documents have security levels. So, basic RAG needs to be extended with access control. We added a permission filter into the retrieval pipeline in this project.

\subhead{2.5 Tool-Augmented Model}

LLMs have a limit. They cannot interact with outside systems or data stores. Tool-augmented language models fix this problem. They let LLMs call APIs, query databases, and run computing tasks. The ReAct framework by Yao et al. (2022) [10] was one of the first designs. It combines reasoning traces and action steps. The model alternately performs reasoning steps (analyzing the current state and deciding what information is needed) and action steps (calling an external tool with specific parameters using a predefined API schema). These alternating steps repeat until the task is finished. ReAct reduces hallucination in comparison to pure language model generation. This is because the model's actions are checked against the outcomes of tool calls it actually makes.

In corporate settings, tool use goes beyond general web search. It includes utilities that are specific to the organization. These utilities include calendar management, resource reservations, internal API calls, and map routing. Our Tool Agent uses deepSeek's large model for intent classification and parameter extraction. Then it routes the request to three specialized handlers. The handlers are for meeting rooms, schedules, and route planning.

\subhead{2.6 Data Security and Local Deployment}

Security and data sovereignty are central concerns when companies adopt AI systems. The common practice is to access LLMs through cloud APIs. In this practice, user queries and context data are sent to servers outside the organization's premises. This is not acceptable for banks where multi-jurisdictional data protection laws demand that customer data must stay within defined geographic and organizational boundaries.

In banking, the Hong Kong Monetary Authority (HKMA) requires that customer information be protected through appropriate safeguards and that institutions retain control over data access and processing. Bender et al. (2021) [11] highlighted broader risks of large-scale language models too. They pointed out that the environmental and data governance costs of large models are not trivial. Organizations must weigh these factors when building AI strategies.

Deploying on-site brings a real challenge. This challenge is the computing cost of running LLM inference. Kwon et al. (2023) [7] came up with a solution. They proposed PagedAttention and the vLLM framework. It achieves near-optimal memory usage by dynamically managing the KV cache with virtual paging. It's based on the key observation that traditional LLM serving systems waste significant GPU memory due to fragmentation and inefficient memory sharing strategies. Inspired by virtual memory and paging techniques in operating systems, PagedAttention partitions the KV cache into fixed-size blocks that can be mapped non-contiguously in memory space.

Karras et al. (2024) [6] provided a comprehensive review of LLM applications in cybersecurity contexts in the big data era. Their analysis synthesized findings from over 100 research papers covering vulnerability detection, incident response, threat intelligence, and secure code generation. Basically, they found that while LLMs show promise in automating many cybersecurity tasks---such as identifying vulnerabilities in source code and generating security patches---current models still struggle with problems like contextual understanding and high false-positive rates in real-world enterprise settings. For this project, these findings reinforce how important it is to adopt a defense-in-depth security architecture instead of relying on LLM reasoning alone.

Our local deployment plan uses Docker Compose. This plan is consistent with the principle of data sovereignty. It also references PagedAttention's insights on optimization. However, its current position in the project is mostly architectural.

\newpage

% ======================================================================
