% CHAPTER 8: CONCLUSION AND FUTURE WORK
% ======================================================================
{\fontsize{18}{22}\selectfont\textbf{8 Conclusion and Future Work}}\par

\vspace{3mm}

\subhead{8.1 Summary of Achievements}

This project presents a multi-agent AI platform for banking digital transformation. It addresses issues such as code generation accuracy, domain knowledge reliability, tool invocation robustness, and the data sovereignty demands unique to the banking industry. Through the collaborative work of three specialized agents, a cross-agent intelligent dispatcher, a five-layer defense architecture, and an on-premise Docker Compose deployment model, the platform provides banking personnel with unified AI capabilities accessible through a single natural language interface.

The Code agent implements a natural-language-to-SQL pipeline backed by a Python LLM inference server, combined with a five-layer SQL whitelist validation mechanism enforcing operation-type restrictions, keyword blacklisting, table/column whitelisting, and query complexity limits. The RAG agent implements an end-to-end enterprise retrieval pipeline, combining document parsing, structure-aware chunking, Milvus vector retrieval, configurable embedding profiles, permission-safe filtering, citation construction, query audit logging, and an OpenAI-compatible LLM generation interface. The Tool agent implements a dual-path design (programmatic REST endpoints and AI intent routing through the DeepSeek LLM) with mock fallback support, providing meeting room management, Redis-based schedule conflict detection, and Amap-integrated route planning.

Above these three agents, the Copilot serves as a cross-page, multi-agent intelligent dispatcher. Its three-tier intent classification pipeline --- a security blocklist, keyword greeting detection, and LLM-based six-category classification --- routes natural language queries to the appropriate agent without requiring the user to understand which agent handles which domain. Multi-turn clarification enables the system to gather missing parameters through follow-up questions. A unified AI provider configuration center, accessible through a single admin UI, eliminates the configuration fragmentation that existed when each agent managed its own LLM settings independently.

The system integration layer provides JWT-based authentication with dual-mode login (password and email verification code), three-tier RBAC with department-level data isolation, HITL document access using a notification-based approval system, a Task Center with asynchronous execution, exponential-backoff retry, and WebSocket real-time progress streaming, and containerized deployment via Docker Compose.

\subhead{8.2 Future Work}

Several directions for future work have been determined. Local ONNX Runtime inference for the Code Agent could reduce HTTP overhead. The Task Center should be upgraded from in-memory queuing to a message broker (RabbitMQ or Redis Streams) for production-grade durability. DevOps enhancements should include Prometheus metrics, Grafana dashboards, distributed tracing, Kubernetes orchestration for multi-node scaling, and automated CI/CD pipelines. The Copilot's intent classifier could benefit from a feedback loop --- tracking whether the dispatched agent actually handled the query successfully and using that signal to refine classification prompts. RBAC extensibility should allow adopting institutions to extend the three-tier role model with custom fine-grained permissions. The platform should be extended to support additional enterprise tools (email, HR systems, document management systems) through a pluggable tool registration mechanism, and to support additional database systems beyond MySQL.

\newpage

% ======================================================================
