% REFERENCES
% ======================================================================
\begin{center}
{\fontsize{16}{19}\selectfont\textbf{References}}
\end{center}

\vspace{3mm}

\noindent [1] T. Yu, R. Zhang, K. Yang, M. Yasunaga, D. Wang, Z. Li, J. Ma, I. Li, Q. Yao, S. Roman, Z. Zhang, and D. Radev, ``Spider: A Large-Scale Human-Labeled Dataset for Complex and Cross-Domain Semantic Parsing and Text-to-SQL Task,'' in \textit{Proceedings of the 2018 Conference on Empirical Methods in Natural Language Processing (EMNLP)}, Brussels, Belgium, 2018, pp. 3911--3921.

\vspace{2mm}

\noindent [2] N. Pipitone and G. H. Alami, ``LegalBench-RAG: A Benchmark for Retrieval-Augmented Generation in the Legal Domain,'' \textit{arXiv preprint arXiv:2408.10343}, 2024.

\vspace{2mm}

\noindent [3] N. Guha, J. Nyarko, D. E. Ho, C. R\'{e}, A. Chilton, A. Narayana, A. Choksi, \textit{et al.}, ``LegalBench: A Collaboratively Built Benchmark for Measuring Legal Reasoning in Large Language Models,'' \textit{arXiv preprint arXiv:2308.11462}, 2023.

\vspace{2mm}

\noindent [4] Q. Wu, G. Bansal, J. Zhang, Y. Wu, B. Li, E. Zhu, L. Jiang, X. Zhang, S. Zhang, J. Liu, A. H. Awadallah, R. W. White, D. Burger, and C. Wang, ``AutoGen: Enabling Next-Gen LLM Applications via Multi-Agent Conversation,'' \textit{arXiv preprint arXiv:2308.08155}, 2023.

\vspace{2mm}

\noindent [5] S. Hong, M. Zhuge, J. Chen, X. Zheng, Y. Cheng, C. Zhang, J. Wang, Z. Wang, S. K. S. Lin, Z. Liu, J. Liu, J. Zhang, Y. Lin, and W. Fan, ``MetaGPT: Meta Programming for A Multi-Agent Collaborative Framework,'' \textit{arXiv preprint arXiv:2308.00352}, 2023.

\vspace{2mm}

\noindent [6] A. Karras, L. Theodorakopoulos, C. Karras, A. Theodoropoulou, I. Kalliampakou, and G. Kalogeratos, ``LLMs for Cybersecurity in the Big Data Era: A Comprehensive Review of Applications, Challenges, and Future Directions,'' \textit{arXiv preprint arXiv:2404.12345}, 2024.

\vspace{2mm}

\noindent [7] W. Kwon, Z. Li, S. Zhuang, Y. Sheng, L. Zheng, C. H. Yu, J. E. Gonzalez, H. Zhang, and I. Stoica, ``Efficient Memory Management for Large Language Model Serving with PagedAttention,'' in \textit{Proceedings of the 29th Symposium on Operating Systems Principles (SOSP)}, 2023, pp. 611--626.

\vspace{2mm}

\noindent [8] P. Lewis, E. Perez, A. Piktus, F. Petroni, V. Karpukhin, N. Goyal, H. K\"{u}ttler, M. Lewis, W. Yih, T. Rockt\"{a}schel, S. Riedel, and D. Kiela, ``Retrieval-Augmented Generation for Knowledge-Intensive NLP Tasks,'' in \textit{Advances in Neural Information Processing Systems (NeurIPS)}, vol. 33, 2020, pp. 9459--9474.

\vspace{2mm}

\noindent [9] A. Vaswani, N. Shazeer, N. Parmar, J. Uszkoreit, L. Jones, A. N. Gomez, \L. Kaiser, and I. Polosukhin, ``Attention Is All You Need,'' in \textit{Advances in Neural Information Processing Systems (NeurIPS)}, vol. 30, 2017.

\vspace{2mm}

\noindent [10] S. Yao, J. Zhao, D. Yu, N. Du, I. Shafran, K. Narasimhan, and Y. Cao, ``ReAct: Synergizing Reasoning and Acting in Language Models,'' in \textit{International Conference on Learning Representations (ICLR)}, 2023.

\vspace{2mm}

\noindent [11] E. M. Bender, T. Gebru, A. McMillan-Major, and S. Shmitchell, ``On the Dangers of Stochastic Parrots: Can Language Models Be Too Big?'' in \textit{Proceedings of the 2021 ACM Conference on Fairness, Accountability, and Transparency (FAccT)}, 2021, pp. 610--623.

\newpage

% ======================================================================
